Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex
working process, and no Time of flight spectra at CUP and SUP

\begin{figure}[t]
%    \vspace{2in}
	\subfloat[Integral fluence rate]{\includegraphics[width=2.5in]{CUPcomparedProkofiev2014linearspaceIFlux.eps}\hspace{\columnwidth}}\\
%    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedLetFluxRADECS.png}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \todo{Show Comparison between Geant4 and MCNPX calculations}
    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCPX calculations~\cite{Prokofiev14}}
    \label{fig:MCComparison}
\end{figure}

>>>>

\begin{figure}[t]
%    \vspace{2in}
	\subfloat[Integral fluence rate]{\includegraphics[width=2.5in]{CUPcomparedProkofiev2014linearspaceIFlux.eps}\hspace{\columnwidth}}\\
%    \vspace{2in}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{CUPcomparedProkofiev2014NormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the Close User Position, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from this work.}
	\label{fig:CUPSpectraComparison}
\end{figure}

\begin{figure}[t]
    \vspace{2in}
    \includegraphics[width=3in]{TOFcomparedLetFluxRADECS.png}
% \todo{Show Comparison between Geant4 and MCNPX calculations}
    \caption{Calculated neutron spectra at the CUP-TOF position, compared to independent MCNPX calculations~\cite{Prokofiev14}}
    \label{fig:MCComparison}
\end{figure}
